Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-28 Scripts/evaluating_pca.Rmd
created clustered tad plots after keeping only top 75% most variable columns

>>>>

  ##Removing zero variance predictors
  ###using caret
  #nzv <- nearZeroVar(data, saveMetrics= TRUE)
  #nzvar <- rownames(nzv[nzv$nzv,])
  #if(length(nzvar) > 0){
  #  data <- data[, -which(colnames(data) %in% nzvar)]
  #}

  ##keeping top 75th percentile variable
  colvariance <- apply(data,2,var)
  thirdquart <- as.numeric(summary(colvariance)[5])
  data <- data[,which(colvariance >= thirdquart)]
